Modeling an Economy with Policy Gradients

### 2019-12-05 paper/paper.tex
Starting RL section of paper

\section{Methods}

@@

The authors feel that they all contributed equally to the work presented. In particular, Andrew Chen implemented the actor-critic reinforcement learning algorithm, Nicholas Hirning implemented the circular flow model architecture, and Rory Lipkis performed hyperparameter optimization and data analysis. All three authors collaborated on implementing and debugging the REINFORCE policy gradient algorithm and other areas of the code.

>>>>

\section{Methods}
\subsection{Problem Framing******}

[multiagent -> individual RL agents]
[describe state]
[describe actions]
[describe rewards]
[parameterizing the demand curve]
[full transparency]

\subsection{RL Algorithms******}
We worked within the realm of policy gradient methods; we chose this family of algorithms

[exploration strategy is built in?]

with large action spaces.

\subsubsection{REINFORCE Policy Gradient******}

@@

The authors feel that they all contributed equally to the work presented. In particular, Andrew Chen implemented the policy gradient and actor-critic algorithms, Nicholas Hirning implemented the circular flow model architecture, and Rory Lipkis performed hyperparameter optimization and data analysis. All three authors collaborated on implementing and debugging the REINFORCE policy gradient algorithm and other areas of the code.
